\begin{thebibliography}{100}
\addcontentsline{toc}{chapter}{Bibliograf\'{\i}a}

\bibitem{libro_esfarm} 
K.Atkinson, Weimin Han
\newblock {\it Spherical Harmonics and Approximations on the Unit Sphere: An Introduction}, 2nd ed.,
\newblock Springer.

\bibitem{libro_gegen}
Gabor Szegö
\newblock{\it Orthogonal Polynomials}
\newblock American Mathematical Society, 1939.

\bibitem{art_grad}
Miguel A. Piñar, Yuan Xu
\newblock{Best Polynomial Approximation on the Unit Ball}

\bibitem{data_mining}
Ian H. Witten,Eibe Frank, \newblock{\it Data Mining Practical Machine Learning Tools and Techniquies}, 2nd edition 
\newblock {Morgan Kaufmann Publishers, 2005.}

\bibitem{boosting}
Y. Freund and R. Schapire,\newblock{ \it Experiments with a new boosting algorithm. In Proceedings of the Thirteenth International
Conference on Machine Learning} 
\newblock pages 148–156, 1996.

\bibitem{rusboost}
\newblock Chris Seiffert, Taghi M. Khoshgoftaar, Jason Van Hulse, Amri Napolitano{\it RUSBoost: Improving Classification Performance when Training Data is Skewed}

\bibitem{cusboost}
 Farshid Rayhan, Sajid Ahmed, Asif Mahbub, Md. Rafsan Jani,
Swakkhar Shatabda,Dewan Md. Farid\newblock{\it CUSBoost: Cluster-based Under-sampling with Boosting for Imbalanced Classification}
\newblock{December 2017}

\bibitem{scikit-learn}
\newblock{\href{http://scikit-learn.org/stable/}{http://scikit-learn.org/stable/}}

\bibitem{xgboost}
\href{http://xgboost.readthedocs.io/en/latest/}{http://xgboost.readthedocs.io/en/latest/}

\bibitem{grid_search}
Kevin Lemagnen \newblock{\it Hyperparameter tuning in XGBoost}
\newblock{\href{https://cambridgespark.com/content/tutorials/hyperparameter-tuning-in-xgboost/index.html}{https://cambridgespark.com/content/tutorials/hyperparameter-tuning-in-xgboost/index.html}}

\bibitem{clasification}
G. Shmueli, N.R. Patel, P.C. Bruce \newblock{\it Data mining for business intelligence}
\newblock{Wiley,2010 (2nd. edition)}
\end{thebibliography}
